---
title: "DRNNAGE Report"
subtitle: "Age-at-Death Analysis"
date: "`r Sys.time()`"
output: 
  pagedown::html_paged:
    toc: true
    number_sections: false
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  cache = FALSE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 6,
  fig.height = 4
)

rinline <- function(code) {
  html <- '<code  class="r">``` `r CODE` ```</code>'
  sub("CODE", code, html)
}

```

```{r}
  htmltools::includeMarkdown('../license.md')
```

## Estimate {.page-break-before}
<br>
```{r, echo = FALSE}
params$tbl_pred
```
<br>  
```{r, echo = FALSE}
params$tbl_int
```
<br>
```{r, echo = FALSE}
params$plt_tg_rum
```

## Explain - Prediction {.page-break-before}
<br>
```{r, echo = FALSE}
params$tbl_ls_pred
```
<br>
```{r, echo = FALSE}
params$tbl_ls_cont
```
## Explain - Model {.page-break-before}
<br>
```{r, echo = FALSE}
params$tbl_ls_summary
```
<br>
```{r, echo = FALSE}
params$tbl_ls_model
```

## Assess {.page-break-before}
<!-- ## Prediction Accuracy Analysis -->
```{r, echo = FALSE, message = FALSE, warning = FALSE}
params$plt_accu
```
<!-- ## Prediction Bias Analysis -->
```{r, echo = FALSE, message = FALSE, warning = FALSE}
params$plt_bias
```
<!-- ## Efficiency Analysis -->
```{r, echo = FALSE, message = FALSE, warning = FALSE}
params$plt_effi
```

## Parameters

| Parameter | Value |
| :--- | ---: |
|Network | `r params$analysis$algorithm`|
|Width | `r params$analysis$width`|
|Depth | `r params$analysis$depth`|
|Gaussian Noise | `r params$analysis$eta`|
|Alpha | `r params$analysis$alpha`|
|Exponent | `r params$analysis$exponent`|
|Seed | `r params$analysis$seed`|

